\mytitile\\~

### 2020-04-16 document.tex
referee answers

@@

	\maketitle
\section{Introduction}

@@

So far, experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics  were 
focused on single artificial 
atoms \cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes (A-T) splittings of 
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs \cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of similar composite structures with intense driving field. While there were studies on dressing 
of multi-atomic systems in a 
cavity \cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with external dressing field is not less attractive since its 
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule \cite{kou2017fluxonium} (SAM). We use two 
Xmon-type \cite{barends2013coherent} 
transmons \cite{koch2007charge} interacting with 
each other through a cavity 
bus \cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar antenna while its state can be 
monitored by joint dispersive readout using the 
same coupling cavity \cite{chow2010detecting}. We 
find that strong interaction with microwaves not 
only results in multiphoton transitions of 
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules \cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We note that there 
were no such experiments with natural molecules, 
which could in principle demonstrate same 
effects, because they lack controllability and 
coherence of superconducting quantum devices, and 
previous studies of SAAs under strong driving field 
either involved just a single atom or have 
demonstrated only the standard spectral 
signatures known from the quantum optics (see 
Appendix \ref{sec:3-level-at}).

Besides its fundamental importance, this 
experiment may be useful for future quantum 
computers: a quantum engineer should account for 
the observed behaviours carefully controlling the 
driving power (for instance, as we will show, the 
bSWAP gate \cite{poletto2012entanglement} is 
directly affected by light dressing).

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs \cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J, 
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled 
to a single notch-type \cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples \cite{majer2007coupling} the transmons and 
allows joint readout  \cite{chow2010detecting} of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown, where the layout of the components is presented. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw'' \cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in color on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

\begin{figure}
	 	\includegraphics[width=\linewidth]{experiment_2}
	\caption{\textbf{(a)} Optical image of 
	the device (false coloured). Two transmons 
	(orange, 1 and blue, 2) are coupled 
	capacitively to a $\lambda/4$ coplanar 
	resonator. Frequency control lines come from 
	both sides, and from below a waveguide for 
	microwave excitation  is connected (green). 
	\textbf{(b)} The equivalent electrical 
	circuit. Tunable Josephson junctions are 
	SQUIDs with magnetic flux control. 
	\textbf{(c)} Frequencies of the fundamental 
	transitions of the transmons $\omega_1(I)$ 
	and $\omega_2(I)$ depending on the current 
	$I$ in an external coil when correctly 
	aligned by the individual flux control lines. 
	In this work, we focus on the area inside the 
	dashed rectangle.}
	\label{fig:experiment}
\end{figure}

\begin{table}
	\begin{ruledtabular}
	\begin{tabular}{rll}
	Parameter & Transmon 1  & Transmon 2\\\hline
	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
	$\alpha/2\pi$ [MHz] & -220 & -220 \\
	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
	$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
	\end{tabular}
	\end{ruledtabular}
	\caption{SAM parameters. Transmons are only 
	different in the frequency tuning range and 
	coherence times measured in the lower sweet 
	spot for the 1\textsuperscript{st} one and in 
	the higher sweet spot for the 
	2\textsuperscript{nd}. The coupling strength 
	$J$ depends on the transmon frequencies and 
	is specified here for $\omega_1/2\pi = 
	\omega_2/2\pi = 5.32$ GHz.}
	\label{tab:parameters}
\end{table}

\subsection{Theoretical background}

@@

Next, we assemble the model for two coupled 
transmons with the corresponding annihilation 
operators $\hat b$ and $\hat c$, the fundamental 
frequencies $\omega_{1,2}$ and anharmonicities 
$\alpha_{1,2}$. The corresponding Hamiltonian of 
the SAM contains two terms representing each 
transmon, two terms representing the interaction 
of each transmon with the driving field at the 
same frequency $\omega_d$, and the 
transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat 
b^\dag)(\hat c+\hat c^{\dagger})$ is the 
transverse interaction between the atoms. 
Strictly speaking, $J = J(\omega_1, \omega_2)$ 
depends on the transmon 
frequencies \cite{koch2007charge}, but we take $J$ 
to be a constant as in \autoref{tab:parameters} 
due to its negligible variation for our range of 
frequencies.

@@

In the following, we will also transform 
\autoref{Hsystem} into the frame rotating with 
both drives by an operator
\begin{equation}
\hat R = \exp[-i t (\omega_d^1 
b^{\dagger}b+\omega_d^2 
c^{\dagger}c)],\label{eq:R}
\end{equation}
arriving at
\begin{equation}
\hat H_R = \hat R^{\dagger}\hat H \hat R -	 
{i}\hat R^{\dagger}\partial_t \hat 
R.\label{eq:rotation}
\end{equation}
Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
\begin{equation}
\begin{aligned}
	\omega_{\{1,2\}} &\rightarrow \Delta_{\{1,2\}} = \omega_{\{1,2\}} - \omega_d^{\{1,2\}},\\
	\hat H_{int} &\rightarrow \hbar J \left[\hat 
	b^\dag \hat c e^{it(\omega_d^1 - \omega_d^2)} 
	+ \hat b \hat c^\dag e^{-it(\omega_d^1 - 
	\omega_d^2)}\right],\\
	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

Besides the unitary evolution, we take into 
account the incoherent processes of relaxation 
and dephasing for each transmon. They are 
modelled using the Lindblad equation with the 
following collapse 
operators \cite{bishop2010circuit}:
\begin{equation}\
\begin{split}
\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, 
\hat b^\dag \hat b,\\
\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, 
\hat c^\dag \hat c,
\end{split}
\end{equation}
where $\gamma_{1,2}$ are the individual 
relaxation rates, and $\gamma_{\phi (1,2)}$ are 
the pure dephasing rates. As one can see, the 
collapse operators are in a separable form, i.e. 
acting only upon a single transmon each. This is 
a valid approach until the coupling strength $J$ 
is not too large \cite{beaudoin2011dissipation}. 
Therefore, the complete evolution equation for 
the system density matrix $\hat \rho$ is
\begin{equation}
\partial_t \hat \rho_{(R)} = \frac{i}{\hbar}[\hat 
\rho, \hat H_{(R)}] + \sum_{\alpha, i} 
\mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho_{(R)} 
= \mathcal{L}\hat\rho_{(R)}, \label{eq:master}
\end{equation}
where $\mathcal{D}[\hat{{O}}]\hat \rho = 
\hat{{O}} \hat \rho \hat{{O}}^\dag - 
\frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat 
\rho\}$ and $\mathcal{L}$ is the Liouville 
superoperator, or the Liouvillian; $_{(R)}$ 
denotes if the Hamiltonian and the corresponding 
solution density matrix are in the rotating frame 
with RWA. In this work, we do not alter the 
dissipator terms when changing the reference 
frame despite that it may not be correct in 
general \cite{shavit2019bridging}.

@@

Numerical simulations are necessary for studying 
\autoref{eq:master} since is does not have an 
analytical solution. We have been using the 
\textit{qutip} \cite{johansson2013qutip} (quantum 
optics toolbox in Python) to simulate the 
dynamics and to find the steady state of the 
system for various parameter combinations of the 
Liouvillian. The source code for the simulations can be found on GitHub \footnote{\url{https://github.com/vdrhtc/Examples/tree/master/transmon-simulations/two_transmons}}.

Two distinct modes of simulation were used in the 
modelling. The first one is for the Liouvillians 
that do not explicitly depend on time. In this 
case, the steady state $\hat \rho_{ss}$ of the 
system should be calculated from the set of 
linear equations obtained from \autoref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} 
\hat \rho = 0
\label{eq:steady}
\end{equation}
This equation is solved with the qutip's 
\textit{steadystate} 
function \footnote{\url{http://qutip.org/docs/4.0.2/guide/guide-steady.html}}.
 This method is applicable when the driving 
frequency for both transmons is the same because 
from \autoref{eq:RWA} follows that $\hat H_{int}$ 
is time independent when $\omega_d^1 = 
\omega_d^2$.

The second mode is required when it is not 
possible to avoid the time-dependence of the 
Liouvillian or if one wants to solve the master 
equation in the laboratory frame. For example, 
when the transmons have to be excited at 
different frequencies ($\omega_d^1 - \omega_d^2 = 
\delta \neq 0$), from \autoref{eq:RWA} we find 
that even in the doubly-rotating frame, $\hat 
H_{int}$ is oscillating, and it is not possible 
to simply drop this term in RWA because it is 
inherent for the SAM. In this case, to find the 
steady state of the system one can employ the 
qutip's \textit{propagator} and 
\textit{propagator\_steadystate} functions. The 
propagator is a completely positive map 
$\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow 
\hat \rho(t_1)$ describing the time evolution of 
the system density matrix; for 
\autoref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering 
superoperator. Since the Liouvillian is periodic 
with a period of $T = 2\pi/\delta$, it is 
possible to calculate the steady state as the 
eigenvector $\hat \rho_{ss}$ of the single-period 
propagator $\Lambda(T, 0)$ corresponding to its 
largest eigenvalue  \cite{dittrich1998quantum, 
rivas2012open}. Upon infinitely many applications 
of $\Lambda$
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

@@

	\includegraphics[width=.495\linewidth]{main_picture_slices}
	\includegraphics[width=.495\linewidth]{stationary}
	\caption{Two-tone spectroscopy: experiment 
	and numerical modelling. \textbf{(a)} 
	Experimental data. Colour shows the real part 
	of complex transmission  through the sample. 
	Two transmons are aligned as in 
	\autoref{fig:experiment}~(c) and form a 
	symmetric picture. Experimental data contain 
	an additional horizontal line from a 
	parasitic resonance interacting with the 
	readout resonator. Three avoided crossings 
	not predicted by the unperturbed model are 
	shown in insets I, II and III; other 
	pronounced features reproduced by the 
	modelling are shown with Arabic markers (see 
	text for description). \textbf{(b)} Numerical 
	simulation reproducing experimental results 
	with labelled transitions (see Section 
	\ref{sec:analysis} for notation). 
	\textbf{(c)} Slices of (a) and (b) at various 
	currents: 0.365 mA (feature III), 0.411 mA 
	(sweet spot), 0.333 mA (feature I); 
	experiment is gray, simulation is black. 
	Spectral lines where only one SAA is excited 
	are highlighted with the corresponding colour 
	from \autoref{fig:experiment}. Rabi 
	frequencies $\Omega_{1,2}$ may be extracted 
	as FWHM of the spectral lines 10 and 01, 
	respectively. \textbf{(d)} Simulated 
	population of the state $\ket{10}$ ($\log_{10} 
	P_{\ket{10}}$ is shown with colour). Lines 
	show various transition frequencies from the 
	unperturbed Hamiltonian. In the legend, the 
	transitions are labelled near the sweet spot current; if 
	elsewhere any two lines form an avoided 
	crossing, the labels should be swapped after 
	the intersection.}
	\label{fig:two-tone}
\end{figure*}

Experiment was conducted as described in Appendix 
\ref{sec:meas_setup}. We use high-power two-tone 
spectroscopy to probe transitions between 
eigenstates of the SAM; the result is shown in 
\autoref{fig:two-tone}~(a). As one can see, some 
new spectral lines are visible besides the 
fundamental ones that were shown in 
\autoref{fig:experiment}~(c). Their frequency 
also depends on the applied current, and at 
several points they become resonant with each 
other. At three pairs of such resonant points, we 
observe distinct features shown in insets marked 
with Roman numbers. Some secondary details are 
shown with Arabic-numbered markers.

>>>>

	\author{E.I. Malevannaya}
	\affiliation{FMN Laboratory, Bauman Moscow 
		State Technical University, Moscow, Russia}
	\affiliation{Dukhov Automatics Research 
		Institute, (VNIIA), Moscow, Russia}

@@

	\vspace*{-5cm}
	\maketitle
\section{Introduction}

@@

So far, there have been many experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics with artificial 
atoms \cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes (A-T) splittings of 
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs \cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of similar composite structures with intense driving field. While there were studies on dressing 
of multi-atomic systems in a 
cavity \cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with external dressing field is no less attractive since its 
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule \cite{kou2017fluxonium} (SAM). We use two 
Xmon-type \cite{barends2013coherent} 
transmons \cite{koch2007charge} interacting with 
each other through a cavity 
bus \cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar waveguide antenna while its state can be 
monitored by joint dispersive readout using the 
same coupling cavity \cite{chow2010detecting}. Examining our high-resolution data, we
find that strong interaction with microwaves not 
only results in rich variety of multiphoton transitions of 
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules \cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We could not find any reports of similar effects in the 
previous studies of SAAs under strong driving field because they
either involved just a single atom \cite{baur2009measurement, 
	sillanpaa2009autler, astafiev2010resonance, 
	novikov2013autler, 
	koshino2013observation, 
	braumuller2015multiphoton, peng2018vacuum, 
	gasparinetti2019two} or have 
demonstrated only the standard spectral 
signatures known from the quantum optics \cite{suri2013observation} (see 
Appendix \ref{sec:3-level-at}). Moreover, most of the previous spectroscopic experiments with coupled transmons were done at low powers and resolved only the most prominent single-photon transitions \cite{majer2007coupling, filipp2011multimode}, or used two distinct excitation frequencies to reach higher energy levels \cite{dicarlo2009demonstration}, or did not study the spectral data with necessary resolution \cite{kounalakis2018tuneable}, or used non-tunable transmons \cite{poletto2012entanglement}. In contrast, we put a tunable system in a new regime of intense driving which allows to discover and quantify both experimentally and theoretically its novel unexplored behaviours. Likewise, we could not find reports of such effects in natural molecules, 
which could in principle be observed there; most probably, this is caused by reduced controllability and 
coherence compared to superconducting quantum devices.

We believe that our results are valuable to the domain of molecular physics and quantum optics beyond just superconducting Josephson systems since the reported effects are universally possible for any kind of light-matter interaction. Given similar conditions, they will emerge in any diatomic molecule regardless of its nature, and modification of molecular spectra using light is now a topic of active research \cite{hertzog2019strong}. In this regard we note that the presented theoretical framework is important, too, as it will be useful in analysis of similar effects in the future. Besides, we consider this experiment to be useful for superconducting quantum 
computing: one should account for 
the observed behaviours carefully controlling the 
driving power (for instance, as we will show, the 
bSWAP gate \cite{poletto2012entanglement} may be 
directly affected by light dressing). Finally, the high-power excitation regime is useful to directly obtain information about higher energy levels of the system while using minimum equipment; this is an important problem that should be addressed to facilitate scaling of control electronics for superconducting quantum processors (see, i.e. \cite{hornibrook2015cryogenic}).

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs \cite{hutchings2017tunable}. Single-transmon parameters determined from spectroscopy: maximal Josephson energies $E^{(1)}_{J, 
\sum}/h = 24.3$ GHz, $E^{(2)}_{J,\sum}/h = 18.3$ GHz, 
charging energies $E^{(1,2)}_C/h = 220$ MHz, SQUID asymmetries $d^{(1,2)} = 0.75$ defined as in \cite{koch2007charge}) coupled 
to a single notch-type \cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples \cite{majer2007coupling} the transmons and 
allows joint readout  \cite{chow2010detecting} of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown, where the layout of the components is presented. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw'' \cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in color on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

\begin{figure}
	 	\includegraphics[width=\linewidth]{experiment_2}
	\caption{\textbf{(a)} Optical image of 
	the device (false colored). Two transmons 
	(orange, 1 and blue, 2) are coupled 
	capacitively to a $\lambda/4$ coplanar 
	resonator. Frequency control lines come from 
	both sides, and from below a waveguide for 
	microwave excitation  is connected (green). 
	\textbf{(b)} The equivalent electrical 
	circuit. Tunable Josephson junctions are 
	SQUIDs with magnetic flux control. 
	\textbf{(c)} A sketch of the frequencies of the fundamental 
	transitions of the transmons $\omega_1(I)$ 
	and $\omega_2(I)$ depending on the current 
	$I$ in an external coil when correctly 
	aligned by the individual flux control lines. 
	In this work, we focus on the area inside the 
	dashed rectangle.}
	\label{fig:experiment}
\end{figure}

\vspace{-.5cm}
\subsection{Quantum-mechanical description}

@@

Next, we assemble the model for two coupled 
transmons with the corresponding annihilation 
operators $\hat b$ and $\hat c$, the fundamental 
frequencies $\omega_{1,2}$ and anharmonicities 
$\alpha_{1,2}$. The corresponding Hamiltonian of 
the SAM contains two terms representing each 
transmon, two terms representing the interaction 
of transmons with driving fields at the 
frequencies $\omega_d^{(1,2)}$, and the 
transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{(1)}+\hat H_{tr}^{(2)}+\hat H_{d}^{(1)}+\hat H_{d}^{(2)}+\hat H_{int},
\end{equation}
where the superscripts numerate the transmons and $\hat H_{int} = \hbar J (\hat b +\hat 
b^\dag)(\hat c+\hat c^{\dagger})$. 
Strictly speaking, $J = J(\omega_1, \omega_2)$ 
depends on the transmon 
frequencies \cite{koch2007charge}, but we take $J$ 
to be a constant due to its negligible variation for our range of frequencies.

@@

In the following, we will also transform 
\autoref{Hsystem} into the frame rotating with 
both drives by an operator
\begin{equation}
\hat R = \exp[-i t (\omega_d^{(1)}
b^{\dagger}b+\omega_d^{(2)} 
c^{\dagger}c)],\label{eq:R}
\end{equation}
arriving at
\begin{equation}
\hat H_R = \hat R^{\dagger}\hat H \hat R -	 
{i}\hat R^{\dagger}\partial_t \hat 
R.\label{eq:rotation}
\end{equation}
After the transformation and application of the RWA
\begin{equation}
\begin{aligned}
	\omega_{1,2} &\rightarrow \Delta_{1,2} = \omega_{1,2} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow \hbar J \left[\hat 
	b^\dag \hat c e^{it(\omega_d^{(1)} - \omega_d^{(2)})} 
	+ \hat b \hat c^\dag e^{-it(\omega_d^{(1)} - 
	\omega_d^{(2)})}\right],\\
	\hat H_{d}^{(1)} &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^{(2)} \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

Besides the unitary evolution, we take into 
account the incoherent processes of relaxation 
and dephasing for each transmon. They are 
modelled using the Lindblad equation with the 
following collapse 
operators \cite{bishop2010circuit}:
\begin{equation}\
\begin{split}
\hat{{O}}_{\gamma}^{(1)} = \sqrt{\gamma^{(1)}}\, \hat b,\ 
\hat{{O}}_{\phi}^{(1)} = \sqrt{\gamma_{\phi}^{(1)}}\, 
\hat b^\dag \hat b,\\
\hat{{O}}_{\gamma}^{(2)} = \sqrt{\gamma^{(2)}}\, \hat c,\ 
\hat{{O}}_{\phi}^{(2)} = \sqrt{\gamma_{ \phi}^{(2)}}\, 
\hat c^\dag \hat c,
\end{split}
\end{equation}
where $\gamma^{(1,2)}$ are the individual 
relaxation rates, and $\gamma_{\phi}^{(1,2)}$ are 
the pure dephasing rates. As one can see, the 
collapse operators are in a separable form, i.e. 
acting only upon a single transmon each which is 
a valid approach as long as the coupling strength $J \ll \omega_{1,2}$ 
 \cite{beaudoin2011dissipation}. 
Therefore, the complete evolution equation for 
the system density matrix $\hat \rho$ is		
\begin{equation}
\partial_t \hat \rho_{(R)} = \frac{i}{\hbar}[\hat 
\rho, \hat H_{(R)}] + \sum_{\substack{\alpha = {\gamma, \phi},\\ i=1,2}} 
\mathcal{D}[\hat{O}_{\alpha}^{(i)}] \hat \rho_{(R)} 
= \mathcal{L}\hat\rho_{(R)}, \label{eq:master}
\end{equation}
where $\mathcal{D}[\hat{{O}}]\hat \rho = 
\hat{{O}} \hat \rho \hat{{O}}^\dag - 
\frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat 
\rho\}$ and $\mathcal{L}$ is the Liouville 
superoperator, or the Liouvillian; $_{(R)}$ 
denotes if the Hamiltonian and the corresponding 
solution density matrix are in the rotating frame 
with RWA. In this work, we do not alter the 
dissipator terms when changing the reference 
frame despite that it may not be correct in 
general \cite{shavit2019bridging}.

We summarize the parameters of the SAM model in \autoref{tab:parameters}. The coherence times $T_1 = 1/\gamma$, $T_2^{*} = 1/(\gamma/2 + \gamma_{\phi})$ were measured independently in the lower and upper sweet spot for transmons 1 and 2, respectively. The remaining parameters were extracted from the fits of the unperturbed model to the observed spectral lines; this procedure will be discussed in more detail in Section \ref{sec:level1}.

@@

Numerical simulations are necessary for studying 
\autoref{eq:master} since is does not have an 
analytical solution. We have been using the 
\textit{qutip} \cite{johansson2013qutip} package to simulate the 
dynamics and to find the steady state of the 
system for various parameter combinations of the 
Liouvillian. The source code for the simulations can be found on GitHub \footnote{\url{https://github.com/vdrhtc/Examples/tree/master/transmon-simulations/two_transmons}}.

Two distinct modes of simulation were used in the 
modelling. The first one is for the Liouvillians 
that do not explicitly depend on time. In this 
case, the steady state $\hat \rho_{ss}$ of the 
system should be calculated from the set of 
linear equations obtained from \autoref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} 
\hat \rho = 0
\label{eq:steady}
\end{equation}
This equation is solved with the qutip's 
\textit{steadystate} 
function \footnote{\url{http://qutip.org/docs/4.0.2/guide/guide-steady.html}}.
 This method is applicable when the driving 
frequency for both transmons is the same because 
from \autoref{eq:RWA} follows that $\hat H_{int}$ 
is time independent when $\omega_d^{(1)} = 
\omega_d^{(2)} = 
\omega_d$.

The second mode is required when it is not 
possible to avoid the time-dependence of the 
Liouvillian or if one wants to solve the master 
equation in the laboratory frame. For example, 
when the transmons have to be excited at 
different frequencies ($\omega_d^{(1)} - \omega_d^{(2)} = 
\delta \neq 0$), from \autoref{eq:RWA} we find 
that even in the doubly-rotating frame, $\hat 
H_{int}$ is oscillating, and it is not possible 
to simply drop this term in RWA because it is 
inherent for the SAM. In this case, to find the 
steady state of the system one can employ the 
qutip's \textit{propagator} and 
\textit{propagator\_steadystate} functions. The 
propagator is a completely positive map 
$\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow 
\hat \rho(t_1)$ describing the time evolution of 
the system density matrix; for 
\autoref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering 
superoperator. Since the Liouvillian is periodic 
with a period of $T = 2\pi/\delta$, it is 
possible to calculate the steady state as the 
eigenvector $\hat \rho_{ss}$ of the single-period 
propagator $\Lambda(T, 0)$ corresponding to its 
largest eigenvalue  \cite{dittrich1998quantum, 
rivas2012open}. Upon infinitely many applications 
of $\Lambda$
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

@@

	\includegraphics[width=.495\linewidth]{main_picture_slices}
	\includegraphics[width=.495\linewidth]{stationary}
	\caption{SAM spectroscopy: experiment 
	and numerical modelling. \textbf{(a)} 
	Experimental data. Color shows the real part 
	of complex transmission  through the sample. 
	Two transmons are aligned as in 
	\autoref{fig:experiment}~(c) and form a 
	symmetric picture. Experimental data contain 
	an additional horizontal line from a 
	parasitic resonance interacting with the 
	readout resonator. Three avoided crossings 
	not predicted by the unperturbed model are 
	shown in insets I, II and III; other 
	pronounced features reproduced by the 
	modelling are shown with Arabic markers (see 
	text for description). \textbf{(b)} Numerical 
	simulation reproducing experimental results 
	with labelled transitions (see Section 
	\ref{sec:analysis} for notation). 
	\textbf{(c)} Slices of (a) and (b) at various 
	currents: 0.365 mA (feature III), 0.411 mA 
	(sweet spot), 0.333 mA (feature I); 
	experiment is gray, simulation is black. 
	Spectral lines where only one SAA is excited 
	are highlighted with the corresponding color 
	from \autoref{fig:experiment}. Rabi 
	frequencies $\Omega_{1,2}$ may be extracted 
	as FWHM of the spectral lines 10 and 01, 
	respectively. \textbf{(d)} Simulated 
	population of the state $\ket{10}$. Lines 
	show various transition frequencies from the 
	unperturbed Hamiltonian. In the legend, the main
	transitions that we will use below are labelled near the sweet spot current; if 
	elsewhere any two lines form an avoided 
	crossing, the labels should be swapped after 
	the intersection. Under label ``others'' we put all the remaining possible transitions (single- and multiphoton) between each pair levels of the system that fall into the relevant frequency range of the plot.}
	\label{fig:two-tone}
\end{figure*}

Experiment was conducted as described in Appendix 
\ref{sec:meas_setup}. We use high-power 
spectroscopy to probe transitions between 
eigenstates of the SAM; the result is shown in 
\autoref{fig:two-tone}~(a). As one can see, some 
new spectral lines are visible besides the 
fundamental ones that were shown in 
\autoref{fig:experiment}~(c). Their frequency 
also depends on the applied current, and at 
several points they become resonant with each 
other. At three pairs of such resonant points, we 
observe distinct features shown in insets marked 
with Roman numbers. Some secondary details are 
shown with Arabic-numbered markers.
